% LaTeX template for Artifact Evaluation V20220119
%
% Original Authors 
% * Grigori Fursin (cTuning foundation, France) 2014-2020
% * Bruce Childers (University of Pittsburgh, USA) 2014
% 
% Modified by
% * Clémentine Maurice (CNRS, France) 2021-2022
% * Cristiano Giuffrida (Vrije Universiteit Amsterdam, Netherlands) 2021-2022
%
% (C)opyright 2014-2022
%
% CC BY 4.0 license
%

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix-2020-09}

\usepackage{hyperref}
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% To add the badges to the final version after notification, first download
% the appropriate `usenixbadges` package version as detailed on the Final
% Artifact Appendix instructions page on the USENIX Security website.
%
% Then, uncomment the following line using the appropriate options:
% \usepackage[available,functional,reproduced]{usenixbadges}
%
% In the options, list the badges that have been awarded to your paper.
% The possible badges are:
%
%  * `available`  --- affix the "Artifacts Available" badge
%  * `functional` --- affix the "Artifacts Functional" badge
%  * `reproduced` --- affix the "Results Reproduced" badge
%
% Example:
%  \usepackage[available,functional]{usenixbadges}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\special{papersize=8.5in,11in}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% When adding this appendix to your paper, 
% please remove the part above
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendix
\section{Artifact Appendix}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% See the Artifact Appendix guidelines page on the USENIX
% Security website to compile the appendix. Please preserve
% the provided Artifact Appendix template as much as
% possible (e.g., keep the original (sub)section names
% and order). 
%
% See also examples of past reproduced papers with a similar Artifact Appendix at: https://cknowledge.io/?q=%22reproduced-papers%22+AND+lib+AND+%28secur*+OR+harden*+OR+mitigat*+OR+defen*+OR+attack*+OR+bug*+OR+vulnerab*%29
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Abstract}

This artifact reproduces distributed systems experiments
that benchmark the \textit{collaborative zkSNARKs} that we evaluate in our
paper.

Some experiments run on Google Cloud Platform, so we will give the evaluators
SSH access to one of our machines which has appropriate credentials to launch
the experiments.

The artifact includes scripts to re-run a limited version of our experiments,
and to re-render our plots.

\subsection{Artifact check-list (meta-information)}

{\small
\begin{itemize}
  \item {\bf Algorithm: } GSZ20 and SPDZ MCP protocols. Groth16, Marlin, and
    PLONK zkSNARKs.
  \item {\bf Compilation: } Rust compiler, nightly.
  \item {\bf Run-time environment: } Linux, some experiments on GCP
  \item {\bf Execution: } A distributed protocol
  \item {\bf How much time is needed to prepare workflow (approximately)?: } 30
    minutes
  \item {\bf How much time is needed to complete experiments (approximately)?: }
    30 minutes
  \item {\bf Publicly available (explicitly provide evolving version
    reference)?: } Yes, at
    \url{https://github.com/alex-ozdemir/multiprover-snark}.
  \item {\bf Archived (explicitly provide DOI or stable reference)?: }
    \url{https://github.com/alex-ozdemir/multiprover-snark/tree/98cc63c7b885ade04989a5505050504ae7f2aac0}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Description}

\subsubsection{How to access}

The source is available at
\url{https://github.com/alex-ozdemir/multiprover-snark/tree/98cc63c7b885ade04989a5505050504ae7f2aac0}.

We will provide access to a machine that can run the experiments.

\subsubsection{Hardware dependencies}

At least 8GB of RAM.

\subsubsection{Software dependencies}

Ubuntu packages: zsh libgmp-dev neovim autoconf pkg-config libtool apache2-dev
apache2 dnsmasq-base protobuf-compiler libprotobuf-dev libssl-dev
libxcb-present-dev libcairo2-dev libpango1.0-dev tmux units r-base

Rust compiler: nightly after 2022-01-31.

Ripgrep

Mahimahi network emulator, patched as described in the source distribution at
\texttt{/mpc-snarks/artifact\_eval.md}

R libraries: ggplot2, dplyr, readr, scales

\subsubsection{Data sets}

N/A

\subsubsection{Models}
N/A

\subsubsection{Security, privacy, and ethical concerns}
N/A

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Installation}

(You can skip this. We'll give you access to a machine with the software set up,
and alternatively to a VM that is already set up.)

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  New machine, at least 8GB RAM, 10GB disk
\end{enumerate}

\begin{itemize}
\tightlist
\item
  Ubuntu 20.04 server
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  Do Ubuntu installation
\end{enumerate}

\begin{itemize}
\tightlist
\item
  username: user password: user
\item
  updating took a while
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  \texttt{apt\ install\ zsh\ libgmp-dev\ neovim\ autoconf\ pkg-config\ libtool\ apache2-dev\ apache2\ dnsmasq-base\ protobuf-compiler\ libprotobuf-dev\ libssl-dev\ libxcb-present-dev\ libcairo2-dev\ libpango1.0-dev\ tmux\ units\ r-base\ virutalbox-guest-utils}
\item
  \texttt{curl\ -\/-proto\ \textquotesingle{}=https\textquotesingle{}\ -\/-tlsv1.2\ -sSf\ https://sh.rustup.rs\ \textbar{}\ sh}
\end{enumerate}

\begin{itemize}
\tightlist
\item
  nightly
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{4}
\tightlist
\item
  \texttt{cargo\ install\ ripgrep}
\item
  Install the mahimahi shell network emulator
\end{enumerate}

\begin{itemize}
\tightlist
\item
  clone it
\item
  apply patches

  \begin{itemize}
  \tightlist
  \item
    empty PICKY\_CXXFLAGS in configure.ac (compiler is pickier now)
  \item
    add mm-rate-to-events to install list in scripts/Makefile.am (need
    this)
  \end{itemize}
\item
  \texttt{./autogen.sh\ \&\&\ ./configure\ \&\&\ make\ -j\ 8}
\item
  \texttt{sudo\ sysctl\ -w\ net.ipv4.ip\_forward=1}
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{6}
\tightlist
\item
  Install R libraries: ggplot2, dplyr, readr, scales
\item
  Set up folder sharing
  \texttt{sudo\ adduser\ user\ vboxsf\ \&\&\ sudo\ systemctl\ enable\ virutalbox-guest-utils.service}
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Experiment workflow}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Give us your public key using HotCRP.
\item
  Wait for us to confirm that we have granted that key access.
\item
  \texttt{ssh\ aeval@128.12.176.8}
\item
  \texttt{cd\ \textasciitilde{}/multiprover-snark/mpc-snarks}
\item
  Run \texttt{git\ clean\ -fd} to clear any existing data.
\item
  Check that \texttt{git\ rev-parse\ HEAD} outputs
  98cc63c7b885ade04989a5505050504ae7f2aac0.
\item
  \texttt{cargo\ build\ -\/-release}
\end{enumerate}

\begin{itemize}
\tightlist
\item
  You can \texttt{cargo\ clean} first to force a clean build.
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{4}
\tightlist
\item
  Optional: run the test suite \texttt{./test.zsh}
\end{enumerate}

\begin{itemize}
\tightlist
\item
  If it exits with a zero return code, it was successful.
\end{itemize}
Now, run the experiments (next section)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evaluation and expected results}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Run all experiments with
  \texttt{time\ ./analysis/collect/artifact\_eval.zsh}
\end{enumerate}

\begin{itemize}
\tightlist
\item
  This should take approximately 24 minutes.
\item
  Alternatively: you can run the experiments one-by-one:

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \tightlist
  \item
    \texttt{time\ ./analysis/collect/bad\_net.zsh\ \textbar{}\ tee\ ./analysis/data/bad\_net.csv}
  \end{enumerate}

  \begin{itemize}
  \tightlist
  \item
    This runs locally and should take approximately 6 minutes
  \end{itemize}

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \setcounter{enumi}{1}
  \tightlist
  \item
    \texttt{time\ ./analysis/collect/weak\_machines.zsh}
  \end{enumerate}

  \begin{itemize}
  \tightlist
  \item
    This runs on GCP and should take approximately 10 minutes
  \end{itemize}

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \setcounter{enumi}{2}
  \tightlist
  \item
    \texttt{time\ ./analysis/collect/Npc.zsh}
  \end{enumerate}

  \begin{itemize}
  \tightlist
  \item
    This runs on GCP should take approximately 8 minutes
  \end{itemize}
\end{itemize}
\begin{enumerate}
  \setcounter{enumi}{1}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Generate all plots: \texttt{./analysis/plotting/artifact\_eval.zsh}
\item
  Copy plots to your machine:
  \texttt{scp\ \textquotesingle{}aeval@128.12.176.8:multiprover-snark/mpc-snarks/analysis/plots/*.pdf\textquotesingle{}\ .}
\item
  Analyze:

  \begin{enumerate}
  \def\labelenumii{\arabic{enumii}.}
  \tightlist
  \item
    Varying constraint counts: mpc.pdf should be comparable to Figure 8

    \begin{itemize}
    \tightlist
    \item
      At large constraint counts, 3PC GSZ should have runtime similar to
      ``Single Prover''. The SPDZ MPCs should have approximately twice
      the runtime.
    \end{itemize}
  \item
    Varying prover count: Npc.pdf should be comparable to Figure 9

    \begin{itemize}
    \tightlist
    \item
      Both SPDZ and GSZ should be parabolas. Slowdown should be
      \textasciitilde2x and \textasciitilde1x respectively for 2
      parties.
    \end{itemize}
  \item
    Varying link capacity: bad\_net.pdf should be comparable to Figure
    10

    \begin{itemize}
    \tightlist
    \item
      Slowdown should be going to \textasciitilde2x as bandwidth
      increases. Plonk should be slower than the others.
    \end{itemize}
  \end{enumerate}
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Experiment customization}

If you want to reproduce the single-machine experiments (those that vary link
capacity using a network emulator) on your machine, follow the directions below.

This is optional. You have already produced this graph on our machine.

\hypertarget{build-the-collaborative-proofs-1}{%
\subsubsection{Build the collaborative
proofs}\label{build-the-collaborative-proofs-1}}

Download the VM here: \url{https://doi.org/10.5281/zenodo.5889564}. User: user.
Password: user.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \texttt{cd\ \textasciitilde{}}
\item
  \texttt{git\ clone\ -b\ artiface-eval\ https://github.com/alex-ozdemir/multiprover-snark}
\item
  \texttt{cd\ multiprover-snark/mpc-snarks}
\item
  \texttt{cargo\ build\ -\/-release}
\item
  Optional: run the test suite \texttt{./test.zsh}
\end{enumerate}

\begin{itemize}
\tightlist
\item
  If it exits with a zero return code, it was successful.
\end{itemize}

\hypertarget{collect-the-data-1}{%
\subsubsection{Collect the data}\label{collect-the-data-1}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \texttt{time\ ./analysis/collect/bad\_net.zsh\ \textbar{}\ tee\ ./analysis/data/bad\_net.csv}
\end{enumerate}

\begin{itemize}
\tightlist
\item
  This should take approximately 6 minutes
\end{itemize}

\hypertarget{make-inspect-the-plots-1}{%
\subsubsection{Make \& inspect the plots}\label{make-inspect-the-plots-1}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Varying numbers of provers
\end{enumerate}

\begin{itemize}
\tightlist
\item
  Run: \texttt{Rscript\ ./analysis/plotting/bad\_net.R}
\item
  Output plot: ./analysis/plots/bad\_net.pdf
\item
  It should be comparable to Figure 10
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Notes}
\vspace{1in}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Version}
%%%%%%%%%%%%%%%%%%%%
% Obligatory.
% Do not change/remove.
%%%%%%%%%%%%%%%%%%%%
Based on the LaTeX template for Artifact Evaluation V20220119.

\end{document}
